Linting Linearity in Core/System FC

### 2023-01-10 report.tex
Continue describing Haskell linearity differences

Linearity in Haskell stands out from linearity in Rust and Idris2 for two
distinct reasons:

\begin{itemize}
    \item Linear types were only added to the language roughly \emph{31 years
        after} Haskell's inception. It is an especially difficult endeavour to
        add linear types to a well-established language with a large library
        ecosystem and many active users, rather than to develop the language
        from the ground up with linear types in mind, and the successful
        approach as implemented in GHC 9.0, the leading Haskell compiler, was
        based on Linear Haskell\cite{linearhaskell}, where a linear type system
        designed with retaining backwards-compatibility and allowing code reuse
        across linear and non-linear users of the same libraries in mind was
        described.
    \item 
\end{itemize}

@@

\section {Introduction}

A história que eu quero contar:

\subsection{Motivation}

>>>>

Linearity in Haskell stands out from linearity in Rust and Idris2 for, at least,
the two following distinct reasons:

\begin{itemize}
    \item Linear types were only added to the language roughly \emph{31 years
        after} Haskell's inception. It is an especially difficult endeavour to
        add linear types to a well-established language with a large library
        ecosystem and many active users, rather than to develop the language
        from the ground up with linear types in mind, and the successful
        approach as implemented in GHC 9.0, the leading Haskell compiler, was
        based on Linear Haskell\cite{linearhaskell}, where a linear type system
        designed with retaining backwards-compatibility and allowing code reuse
        across linear and non-linear users of the same libraries in mind was
        described.
    \item Linear types permeate Haskell down to (its) \textbf{Core}, the intermediate
        language Haskell is desugared to. \textbf{Core} is a very small
        explicitly typed language to which multiple Core-to-Core optimizing
        transformations are applied in succession. The final Core program can be
        typechecked very fast (because of the explicit type annotations) and
        doing so serves as a sanity check to the correction of the
        source transformations. If the resulting optimized Core program doesn't
        typecheck, something \emph{very wrong} has happened in a transformation!
\end{itemize}

Even though Linear Haskell was successful in integrating linear types in an
existing language 
% In spite of the smooth integration of linear types in an existing language
with regard to backwards compatibility and (re)usability,

The advent of linear types in Haskell bring forth

@@

\section{Motivation}
